Tracing the Meta-Level: PyPy's Tracing JIT Compiler

### 2009-04-08 talk/icooolps2009/paper.tex
more tweaks to the benchmark section

To test the technique on a more realistic example, we did some
preliminary benchmarks with PyPy's Python interpreter. The function we
benchmarked as well as the results can be seen in Figure
\ref{fig:bench-python}. The function is a bit arbitrary but executing it is
still non-trivial, as a normal Python interpreter needs to dynamically dispatch
nearly all of the involved operations (like indexing into the tuple, addition
and comparison of \texttt{i}). We benchmarked PyPy's Python interpreter with the
JIT disabled, with the JIT enabled and
CPython\footnote{\texttt{http://python.org}} 2.5.4 (the reference implementation of
Python).

@@

\begin{figure}
\label{fig:bench-example}
{\small
\begin{verbatim}
def f(a):
    t = (1, 2, 3)
    i = 0
    while i < a:
        t = (t[1], t[2], t[0])
        i += t[0]
    return i
\end{verbatim}
}
\noindent
\begin{tabular}{|l|l|r|r|}
\hline
& &Time (s) &speedup\\
\hline
1 &Compiled to C, no JIT &23.44 $\pm$ 0.07 &1.00\\
2 &Compiled to C, with JIT &3.58 $\pm$ 0.05 &6.54\\
3 &CPython 2.5.4 &4.96 $\pm$ 0.05 &4.73\\
\hline
\end{tabular}

>>>>

\begin{figure}[h]
\label{fig:bench-example}
{\small
\begin{verbatim}
def f(a):
    t = (1, 2, 3)
    i = 0
    while i < a:
        t = (t[1], t[2], t[0])
        i += t[0]
    return i
\end{verbatim}
}
\noindent
\begin{tabular}{|l|l|r|r|}
\hline
& &Time (s) &speedup\\
\hline
1 &Compiled to C, no JIT &23.44 $\pm$ 0.07 &1.00\\
2 &Compiled to C, with JIT &3.58 $\pm$ 0.05 &6.54\\
3 &CPython 2.5.4 &4.96 $\pm$ 0.05 &4.73\\
\hline
\end{tabular}

To test the technique on a more realistic example, we did some
preliminary benchmarks with PyPy's Python interpreter. The function we
benchmarked as well as the results can be seen in Figure
\ref{fig:bench-python}. While the function may seem a bit arbitrary, executing it is
still non-trivial, as a normal Python interpreter needs to dynamically dispatch
nearly all of the involved operations, like indexing into the tuple, addition
and comparison of \texttt{i}. We benchmarked PyPy's Python interpreter with the
JIT disabled, with the JIT enabled and
CPython\footnote{\texttt{http://python.org}} 2.5.4 (the reference implementation of
Python).

@@
